---
layout: 12pt
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage[document]{ragged2e}
bibliography: ~/Dropbox/Bibliography/CommunitySynchrony.bib
csl: components/ecology.csl

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: false
fontsize: 12pt
geometry: margin=1in

---
```{r caching, include=FALSE}
library("methods")
library("knitr")
basename <- "ms_communitySynchrony"
opts_chunk$set(fig.path = paste("components/figure/", basename, "-", sep=""),
               cache.path = paste("components/cache/", basename, "/", sep=""))
opts_chunk$set(cache = 2)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, 
               comment = NA, verbose = TRUE, echo=FALSE)

# PDF-based figures
opts_chunk$set(dev='pdf')
```


# Environmental responses synchronize population dynamics in five semi-arid grasslands, but not completely

\renewcommand*{\thefootnote}{\fnsymbol{footnote}}

Andrew T. Tredennick\footnote{Correspondance: atredenn@gmail.com}\textsuperscript{1}, Claire de Mazancourt\textsuperscript{2}, Michel Loreau\textsuperscript{2}, \newline Stephen Ellner\textsuperscript{3}, and Peter B. Adler\textsuperscript{1}

\textit{\small{\textsuperscript{1}Department of Wildland Resources and the Ecology Center, 5230 Old Main Hill, Utah State University, Logan, Utah 84322 USA}}

\textit{\small{\textsuperscript{2}Centre for Biodiversity Theory and Modelling, Experimental Ecology Station, Centre National de la Recherche Scientifique, Moulis, 09200, France}}

\textit{\small{\textsuperscript{3}Department of Ecology and Evolutionary Biology, Cornell University, Ithaca, NY 14853, USA}}

\renewcommand*{\thefootnote}{\arabic{footnote}}
\setcounter{footnote}{0}



Abstract
-------------
Temporal asynchrony among interacting species is an important mechanism through which species richness can stabilize biomass production through time. 
While asynchrony is a key mechanism linking biodiversity and ecosystem function, empirical support for the prevalance species asynchrony is mixed, and no studies have rigorously disentangled the forces driving species (a)synchrony in nature. 
Theory identifies three drivers of species synchrony: inter- and intraspecific density dependence sychronizes dynamics, demographic stochasticity desynchronizes dynamics, and environmental forcing can either synchronize or desynchronize poplation dynamics depending on the correlation of species-specific environmental responses. 
Here we use stochastic population models fit using long term datasets from five semi-arid grasslands to identify the forces that increase or decrease species synchrony through time. 
We find that the trophically-similar grass species in our dataset have population dynamics that are synchronized by similar responses to environmental fluctuations. 
Species interactions tend to be weak, so removing interspecific competition did not reduce synchrony. 
The effect of demographic stochasticity depended on the spatial scale of our modeling; demographic stochasticity was strongest in small populations and was able to modestly counteract the synchronizing effect of the environment. 
Although we found that similar responses to environmental fluctuations synchronized species, dynamics were not completly synchronous. 
We conclude that niche differentiation among species is strong enough to reduce the synchronizing effect of coupled density dependence via competition, but this is countered by the synchronizing effect of similar environmental responses. 
The next frontier is to identify the specific environmental drivers of species synchrony to inform predictive efforts.  

__Keywords__: synchrony, compensatory dynamics, environmental stochasticity, demographic stochasticity, stability

<!-- \setlength{\parindent}{5ex} -->

Introduction
------------
All populations fluctuate through time as a result of density-dependence (inter and intraspecific interactions), demographic stochasticity, and fluctuating environmental forces [@Lande2003; @Loreau2008a; @Mutshinda2009; @Gonzalez2009].
Population fluctuations play integral roles at the community and ecosystem levels by creating opportunities for coexistence [@Chesson2000a] and by stabilizing aggregate properties like annual biomass production [@Hector2010; @Loreau2013; @DeMazancourt2013a; @Hautier2014].
In both cases (species coexistence and ecosystem stability), temporal niche differentiation driven by species-specific responses to environmental conditions is necessary to create asynchrounous population dynamics.
However, detecting and interpreting species asynchrony in natural systems has been plagued by methodological issues, and few have attempted to decompose the drivers of species synchrony.
Thus, we lack general answers to two fundamental questions that have fascinated ecologists for decades: (1) How (a)synchronous are interacting populations in natural ecosystems? and (2) What drives temporal (a)synchrnous dynamics in the real world?

The seminal study by @Houlahan2007 suggested that asynchronous population dynamics are rare because they found generally positive correlations in species' abundances through time across a large number of ecosystems.
The conclusion of @Houlahan2007, that abiotic factors synchronize species' abundances, rests on the implicit assumption that species will fluctuate independently in the absence of temporal niche differences.
Thus, if populations are observed to covary positively through time, then the environment must be driving such synchronization.
However, the null hypothesis of independent fluctuations is the incorrect starting point from which to judge spceies synchrony.

All organisms exist in variable environments, and those that coexist on similar resources should be expected to respond to the environment in similar ways.
Based on such a proposition, @Loreau2008a suggest that the true null hypothesis is that coexisting species should fluctuate synchronously, not independently, in the absence of temporal niche differenatiation.
Then, the judgment of whether species fluctate synchronously or not depends on the degree to which observed dynamics deviate from perfect synchrony.
In such a light, Houlahan et al.'s (2007) results can be viewed very differently.
However, Houlahan et al.'s (2007) meausure of compensatory dynamics was summed species covariances through time.
Summed covariances have no upper or lower bound, making it difficult to interpret their results based on deviations from perfect synchrony.
In the end, the fact that few communities exhibited negative summed covariance yields little insight as to whether communities tend to be sychronized by environmental forces or not.

Aside from issues relating to the null expectation of species synchrony, disentangling the factors that drive species syncrony is difficult.
Observational timeseries of species' abundances allows easy quantification of summed covariances [@Houlahan2007] or species synchrony [@Gross2014], but quantifying the relative influence of density-dependence, demographic stochasticity, and environmental stochasticity remains a challenge.
Indeed, to our knowledge, only one other study has attempted to separate the influences of density-dependence and environmental stochasticity [@Mutshinda2009].
@Mutshinda2009 used a statistical technique to decompose synchrony of species' abundances calculate from five time series.
They found that the effect of environmental forcing on temporal dynamics is much stronger than that of interspecific interactions, across all taxa they analyzed [@Mutshinda2009].
However, to link environmental forcing to species synchrony, @Mutshinda2009 examined the correlations among species' environmental responses.

In this paper, we seek to overcome the limitations of previous studies by explicitly testing theory on all the drivers of species synchrony using empirically-based multi-species population models that include the effects of density-dependence, environmental stochasticity, and demographic stochasticity.
Our theoretical framework is that of @Loreau2008a, which defines expectations for the effects of density-dependence, environmental stochasticity, and demographic stochasticity on species synchrony.
We confront theoretical expectations with model-based analyses of community time series from five semi-arid grasslands [@Chu2015].
Our objectives were to (1) reproduce observed species synchrony using multi-species population models, (2) determine the relative influences of environmental stochasticity and interspecific interactions on species synchrony in large populations immune to demographic stochasticity, and (3) determine how dempographic stochasticity augments the influence of the environment and interspecific interactions across a range of populations sizes.
To achieve our objectives, we analyzed spatially-implicit integral projection models (IPMs) and spatially-explicit individually-based models (IBMs) fit to demographic data from each our study sites.
We first show that the models are able to reproduce observed synchrony of species' per capita growth rates and then perturb the models to include/exclude the factors to drive synchrony, as identified by theory.
We used the IPM to model large populations that are immune to demographic stochasticity to isolate the influence of environmental stochasticity; we used the IBM to model populations where demographic stochasticity is present.

Theoretical expectations
------------------------
@Loreau2008a derived a statistic to measure community-wide synchrony of per capita population growth rates:


\begin{equation}
\phi_r = \frac{\sigma^{2}_{T}}{(\sum_{i}\sigma_{r_{i}})^{2}}
\end{equation}


where $\sigma_{r_{i}}$ is the temporal variance of species *i*'s per capita population growth rate ($r_i$) and $\sigma^{2}_{T}$ is the temporal variance of the aggregate community-level growth rate. The statistic is bounded at 0 and 1, where 0 indicates perfect asynchrony and 1 indicates perfect synchrony. When applied to a neutral model where species have perfect niche overlap but have independent demographic and environmental fluctuations through time,  expected synchrony ($\phi_r$) is defined as:

\begin{equation}
\phi_r = \frac{\sigma^{2}_{c} + \sigma^{2}_{e} + \sigma^{2}_{d}/(SN)}{[(1/S)(\sum_{i}\sqrt{\sigma^{2}_{c} + \sigma^{2}_{e} + \sigma^{2}_{d}/(N)})]^2}
\end{equation}

where $\sigma^{2}_{c}$ is the temporal variance of per capita population growth rates due to regulation of community size (density-dependence), $\sigma^{2}_{e}$ is environmental variance, and $\sigma^{2}_{d}$ is demographic variance. *S* is the species richness of the focal community and *N* is the harmonic temporal mean of either the entire community (no subscript in numerator) or species *i* (with subscript in denominator). 

Loreau and de Mazancourt show that when demographic stochasticity is weak relative to community regulation and environmental forcing ($\sigma^{2}_{c}+\sigma^{2}_{e} >> \sigma^{2}_{d}/N_i$), $\phi_r \approx 1$ meaning species are expected to fluctuate synchronously. At the other limit, where environmental forcing and community regulation are strong relative to demographic stochasticity ($\sigma^{2}_{c}+\sigma^{2}_{e} << \sigma^{2}_{d}/N_i$), species are expected to fluctuate independently, and $\phi_r \approx 1/S$ or:

\begin{equation}
\phi_{r} = \frac{ \sum_{i=1}^{N}{\sigma_{i}^2} } { \left(\sum_{i=1}^{N}{\sigma_{i}} \right)^2 }.
\end{equation}

Based on the above theory, we expect synchrony in a community where only demographic stochasticity is operating on top of independent fluctuations to be $1/S$. 

Data and Methods
----------------
## Study sites and species
In the early 20th century, several range experiment stations in the western U.S. began mapping permanent quadrats, and conducted annual censuses for decades. 
We use such long-term demographic data sets from five semiarid grasslands in the western United States (described in detail by Chu and Adler 2015).
Each study site includes a set of 1-$\text{m}^2$ permanent quadrats within which all individual plants were identified and mapped annually using a pantograph (Hill 1920).
The resulting mapped polygons represent basal cover for grasses and canopy cover for shrubs.
Data come from the Sonoran desert in Arizona (Anderson et al. 2012), sagebrush steppe in Idaho (Zachmann et al. 2010), southern mixed prairie in Kansas (Adler et al. 2007), northern mixed prairie in Montana (Anderson et al. 2011), and Chihuahuan desert in New Mexico (Anderson et al. in preparation, Chu and Adler 2015).

Chu and Adler describe the selection of focal species in each data set, so we offer a brief explanation here.
Focal species needed to comply with two criteria: (1) be common enough to provide a large sample size for model fitting and (2) co-occur with other focal species often enough to allow us to describe species interactions within the model.
Thus, Chu and Adler (2015) chose species that occurred in at least 20% of years and then used Nonmetric Multidimensional Scaling (NMDS) to identify quadrats with a similar composition of these candidate species.

## Analytical approach
While the observational data allows us to directly calculate species synchrony within the community, it is impossible to isolate the contributions of demographic and environmental stochasticity on species synchrony based on the data alone. 
So we now turn to a empirically-based modeling approach where we can turn species' interactions and demographic and environmental stochasticity on/off. 
We use two models: (1) an environmentally stochastic Integral Projection Model (IPM) and (2) a demographically and environmentally stochastic Individual Based Model (IBM).
Both models are driven by the same vital rate regressions for survival, growth, and recreuitment.
We use the IPM to explore the drivers of synchrony assuming a large population where demographic stochasticity is weak or absent.
We use the IBM to isolate the effect of demographic stochasticity and to examine how demographic and environmental stochasticity interact as population size increases (i.e., as the effect of demographic stochasticity weakens).
The use of two model types (IPM and IBM) is the only way to isolate the effects of environmental stochasticity (an IPM with no demographic stochasticity) and demographic stochasticity (an IBM with no environmental stochasticity).

## Statistical models for survival, growth, and recruitment
### Survival and growth
We modeled survival probability and growth on individual genets as a function of genet size, the crowding experienced by the focal genet from both heterospecific and conspecific genets in its neighborhood (described below), temporal varation among years, and spatial variation among quadrat groups. Groups are sets of quadrats located in close proximity within a pasture or grazing exclosure).

We follow the approach of Chu and Adler (2015) to estimate crowding, assuming that the crowding experienced by a focal genet depends on distance to each neighbor genet and the neighbor's size, _u_:

\begin{equation}
w_{ijm,t} = \sum_k e^{-\delta_{jm}d_{ijkm,t}^{2}}u_{km,t}.
\end{equation}

In the above, $w_{ijm,t}$ is the crowding that genet _i_ of species _j_ in year _t_ experiences from neighbors of species _m_. The spatial scale over which species _m_ neighbors exert influence on any genet of species _j_ is determined by $\delta_{jm}$. The function is applied for all _k_ genets of species _m_ that neighbor the focal genet at time _t_, and $d_{ijkm,t}$ is the distance between genet _i_ in species _j_ and genet _k_ in species _m_. When $k=m$, the effect is intraspecific crowding. We use regression-specific (survival and growth) $\delta$ values estimated by Chu and Adler (2015).

### Recruitment
We model recruitment as a function of plot-level cover, temporal varation among years, and spatial variation among quadrat groups. 


## Integral projection models (IPM)
### Model structure
We built an environmentally and demographically stochastic integral projection model (IPM), where either environmental or demographic stochasticity can be turned off. Our IPM follows the specification of Chu and Adler (2015) where the population of species _j_ is a density function $n(u_{j},t)$ giving the density of sized-_u_ genets at time _t_. Genet size is on the natural log scale, so that $n(u_{j},t)du$ is the number of genets whose area (on the arithmetic scale) is between $e^{u_{j}}$ and $e^{u_{j}+du}$. So, the density function for any size _v_ at time $t+1$ is

\begin{equation}
n(v_{j},t+1) = \int_{L_{j}}^{U_{j}} k_{j}(v_{j},u_{j},\bar{\bold{w_{j}}}(u_{j}))n(u_{j},t)
\end{equation}

where $k_{j}(v_{j},u_{j},\bar{\bold{w_{j}}})$ is the population kernal that describes all possible transitions from size $u$ to $v$ and $\bar{\bold{w_{j}}}$ is a vector of estimates of average crowding experienced from all other species by a genet of size $u_j$ and species $j$. The integral is evaluated over all possible sizes between predefined lower (_L_) and upper (_U_) size limits that extend beyond the range of observed genet sizes.

The population kernal is defined as the joint contributions of survival (_S_), growth (_G_), and recruitment (_R_):

\begin{equation}
k_{j}(v_{j},u_{j},\bar{\bold{w_{j}}}) = S_j(u_j, \bar{\bold{w_{j}}}(u_{j}))G_j(v_{j},u_{j},\bar{\bold{w_{j}}}(u_{j})) + R_j(v_{j},u_{j},\bar{\bold{w_{j}}}),
\end{equation}

which, said plainly, means we are calculating growth (_G_) for individuals that survive (_S_) from time _t_ to _t+1_ and adding in newly recruited (_R_) individuals of an average sized one-year-old genet for the focal species. Our stastical model for recruitment (_R_, described below) returns the number of new recruit produced per quadrat. Following previous work, we assume that fecundity increases linearly with size ($R_j(v_{j},u_{j},\bar{\bold{w_{j}}}) = e^{u_j}R_j(v_{j},\bar{\bold{w_{j}}})$) to incorporate the recruitment function in the spatially-implicit IPM.

### Model simulations
Our interest is in the (de)synchronizing effects of either demographic or environmental stochasticity. To look at these effects, we run three types of model simulations: (1) demographic stochasticity only, (2) environmental stochasticity only, and (3) both. Environmental stochasticity is implemented by drawing random year effects for the vital rate regressions. We can model a constant environment by simply using vital rate regressions with mean coefficient values. To include demographic stochasticity we treat survival as a binomial process and recruitment as a poisson process in the IPM[^stoch]. See Figure 2 for example model runs.

[^stoch]: This is the crux of the matter here, we need to implement the Poisson approximation at the iteration matrix stage.

Results
-------
## Observed and expected synchrony
Our first task was to calculate the observed and expected community synchrony at each of our study sites. Observed synchrony ($\phi_r$) is calculate using equation 1 and expected synchrony ($\text{E}(\phi_r)$) is simply $1/S$ or equation 3. Expected synchrony under indpendent fluctuations is lower than the observed synchrony at every site (Table 1). This implies that demographic stochasticity is weak relative to community regulation and environmental forcing ($\sigma^{2}_{c}+\sigma^{2}_{e} >> \sigma^{2}_{d}/N_i$). Thus, some combination of density-dependence (species interactions) and environmental forcing are synchronizing population dynamics. To isolate those effects, we turn to our simulation results from the IPMs.

## Effect of removing demographic and environmental stochasticity
At four of our five study areas, the presence of environmental stochasticity via random year effects on vital rate regressions increased community synchrony of per capita population growth rates (Figure 1). Only at the Montana site (Northern Mixed Prairie) did incorporating species' responses to environmental conditions decrease community synchrony. However, even with similar responses to environmental conditions, community synchrony did not reach 1 at any of the sites. Thus, there remains sufficiently strong temporal niche differences to drive the community away from perfect sychrony. 

Theory predicts that demographic stochasticty is the only force that, in isolation, can desynchronize population dynamics. However, theory also predicts that demographic stochasticity is likely unable to counteract the synchronizing effect of environmental forces. Our results support this prediction in the cases where environmental stochasticity is a synchronizing force (compare ENV and ENVDEMO bars in Figure 1).

\newpage{}


Tables
------

\singlespacing

Table 1: Site descriptions and focal species.
\footnotesize

| Site Name | Biome | Location (Lat, Lon) | Obs. Years | Species |
| --------- | ----- | ------------------- | ---------- | ------- |
| Arizona | Sonoran Desert | 31&deg;50' N, 110&deg;53' W | 1915-1933 | *Bouteloua eriopoda* |
| | | | | *Bouteloua rothrockii* |
| Idaho | Sagebrush steppe | 44.2&deg; N, 112.1&deg; W | 1926-1957 | *Artemisia tripartita* |
| | | | | *Pseudoroegneria spicata* |
| | | | | *Hesperostipa comata* |
| | | | | *Poa secunda* |
| Kansas | Southern mixed prairie | 38.8&deg; N, 99.3&deg; W | 1932-1972 | *Bouteloua curtipendula* |
| | | | | *Bouteloua hirsuta* |
| | | | | *Schizachyrium scoparium* |
| Montana | Northern mixed prairie | 46&deg;19' N, 105&deg;48' W | 1926-1957 | *Bouteloua gracilis* |
| | | | | *Hesperostipa comata* |
| | | | | *Pascopyrum smithii* |
| | | | | *Poa secunda* |
| New Mexico | Chihuahuan Desert | 32.62&deg; N, 106.67&deg; W | 1915-1950 | *Bouteloua eriopoda* |
| | | | | *Sporobolus flexuosus* |

\normalsize

\pagebreak{}

```{r load_libs, echo=FALSE, message=FALSE, warning=FALSE}
library(communitySynchrony)
library(plyr)
library(reshape2)
library(synchrony)
library(ggplot2)
library(xtable)
library(gridExtra)
library(RColorBrewer)
```

```{r get_all_data, echo=FALSE}
site <- "Kansas"
spp_list <- c("BOCU","BOHI","SCSC")
num_spp <- length(spp_list)
ks_data <- data.frame(quad=NA, year=NA, totCover=NA, species=NA)
for(dospp in 1:num_spp){ #loop through species to read in data
  spp_now <- spp_list[dospp]
  quad_file <- paste("../data/", site,"/",spp_now,"/quadratCover.csv",sep="")
  spp_data <- read.csv(quad_file)
  spp_data$species <- spp_now
  ks_data <- rbind(ks_data, spp_data)
} #end species looping for raw data
ks_data <- ks_data[2:nrow(ks_data),] #remove first NA row

tmp1<-which(ks_data$quad_data=="q25" & (ks_data$year<35 | ks_data$year>62))
tmp2<-which(ks_data$quad_data=="q27")
tmp3<-which(ks_data$quad=="q28")
tmp4<-which(ks_data$quad=="q30")
tmp5<-which(ks_data$quad=="q31" & (ks_data$year<35 | ks_data$year>39))
tmp6<-which(ks_data$quad=="q32" & (ks_data$year<35 | ks_data$year>41))
tmp<-c(tmp1,tmp2,tmp3,tmp4,tmp5,tmp6)
ks_data<-ks_data[-tmp,]

# exclude the records later than 1968, to keep the same random year effect...
ks_data<-subset(ks_data,year<68)


site <- "Idaho"
spp_list <- sort(c("PSSP","HECO","POSE","ARTR"))
num_spp <- length(spp_list)
id_data <- data.frame(quad=NA, year=NA, totCover=NA, species=NA)
for(dospp in 1:num_spp){ #loop through species to read in data
  spp_now <- spp_list[dospp]
  quad_file <- paste("../data/", site,"/",spp_now,"/quadratCover.csv",sep="")
  spp_data <- read.csv(quad_file)
  spp_data$species <- spp_now
  id_data <- rbind(id_data, spp_data)
} #end species looping for raw data
id_data <- id_data[2:nrow(id_data),] #remove first NA row
# id_data <- subset(id_data, species!="ARTR") #take out the shrub


site <- "Montana"
spp_list <- sort(c("BOGR","HECO","PASM","POSE"))
num_spp <- length(spp_list)
mt_data <- data.frame(quad=NA, year=NA, totCover=NA, species=NA)
for(dospp in 1:num_spp){ #loop through species to read in data
  spp_now <- spp_list[dospp]
  quad_file <- paste("../data/", site,"/",spp_now,"/quadratCover.csv",sep="")
  spp_data <- read.csv(quad_file)
  spp_data$species <- spp_now
  mt_data <- rbind(mt_data, spp_data)
} #end species looping for raw data
mt_data <- mt_data[2:nrow(mt_data),] #remove first NA row



site <- "NewMexico"
spp_list <- sort(c("BOER","SPFL"))
num_spp <- length(spp_list)
nm_data <- data.frame(quad=NA, year=NA, totCover=NA, species=NA)
for(dospp in 1:num_spp){ #loop through species to read in data
  spp_now <- spp_list[dospp]
  quad_file <- paste("../data/", site,"/",spp_now,"/quadratCover.csv",sep="")
  spp_data <- read.csv(quad_file)
  spp_data$species <- spp_now
  nm_data <- rbind(nm_data, spp_data)
} #end species looping for raw data
nm_data <- nm_data[2:nrow(nm_data),] #remove first NA row



site <- "Arizona"
spp_list <- sort(c("BOER","BORO"))
num_spp <- length(spp_list)
az_data <- data.frame(quad=NA, year=NA, totCover=NA, species=NA)
for(dospp in 1:num_spp){ #loop through species to read in data
  spp_now <- spp_list[dospp]
  quad_file <- paste("../data/", site,"/",spp_now,"/quadratCover.csv",sep="")
  spp_data <- read.csv(quad_file)
  spp_data$species <- spp_now
  az_data <- rbind(az_data, spp_data)
} #end species looping for raw data
az_data <- az_data[2:nrow(az_data),] #remove first NA row
```

```{r get_all_synch, echo=FALSE, include=TRUE}
out_ks <- get_comm_synchrony(ts_data = ks_data)
out_id <- get_comm_synchrony(ts_data = id_data)
out_mt <- get_comm_synchrony(ts_data = mt_data)
out_nm <- get_comm_synchrony(ts_data = nm_data)
out_az <- get_comm_synchrony(ts_data = az_data)
```

```{r synchrony_table, echo=FALSE, include=TRUE, results='asis', message=FALSE}
get_table_metrics <- function(output){
  tmp <- output
  exp_tmp <- round(tmp$pgr_expected_synch_ind_flucts, 2)
  obs_tmp <- round(as.numeric(tmp$pgr_synchrony[1]), 2)
  demo_tmp <- exp_tmp - obs_tmp
  return(c(obs_tmp, exp_tmp, demo_tmp))
}

table_data <- as.data.frame(rbind(get_table_metrics(out_ks),
                                  get_table_metrics(out_id),
                                  get_table_metrics(out_mt),
                                  get_table_metrics(out_nm),
                                  get_table_metrics(out_az)))
table_data$Site <- c("Kansas", "Idaho", "Montana", "New Mexico", "Arizona")
table_data <- table_data[,c("Site", "V1", "V2", "V3")]
table_data$spp <- c(length(unique(ks_data$species)),
                    length(unique(id_data$species)),
                    length(unique(mt_data$species)),
                    length(unique(nm_data$species)),
                    length(unique(az_data$species)))
colnames(table_data) <- c("Site",
                          "$\\phi_{r}$", 
                          "$\\text{E}(\\phi_{r})$", 
                          "$\\text{E}(\\sigma_{d})$",
                          "Species richness")

synch_cap <- "Observed and expected synchrony among species' per capita growth rates and expected effect of demographic stochasticity on observed synchrony. Species richness values reflect the number of species analyzed from the community, not the actual richness."
print(xtable(table_data, caption = synch_cap),
      caption.placement="top",
      include.rownames = F, 
      sanitize.colnames.function = identity,
      comment=FALSE)
```

```{r time_series_fig, echo=FALSE, include=TRUE, fig.height=7, fig.cap="Observed time series of mean percent cover (averaged over quadrats for each year) and per capita growth rates for each species at each site.", eval=FALSE}
# out_ks$percent_cover$site <- "Kansas"
# out_id$percent_cover$site <- "Idaho"
# out_mt$percent_cover$site <- "Montana"
# out_nm$percent_cover$site <- "New Mexico"
# out_az$percent_cover$site <- "Arizona"
# cover_data <- rbind(out_ks$percent_cover, out_id$percent_cover,
#                     out_mt$percent_cover, out_nm$percent_cover, 
#                     out_az$percent_cover)
# 
# out_ks$growth_rates$site <- "Kansas"
# out_id$growth_rates$site <- "Idaho"
# out_mt$growth_rates$site <- "Montana"
# out_nm$growth_rates$site <- "New Mexico"
# out_az$growth_rates$site <- "Arizona"
# pgr_data <- rbind(out_ks$growth_rates, out_id$growth_rates,
#                   out_mt$growth_rates, out_nm$growth_rates, 
#                   out_az$growth_rates)
# all_spp <- unique(pgr_data$species)
# color_match <- data.frame(species = all_spp,
#                           color = brewer.pal(11,"Paired"))
# pgr_data <- merge(pgr_data, color_match, by = "species")
# cover_data <- merge(cover_data, color_match, by="species")
# 
# cover_plot <- ggplot(data=cover_data, aes(x=(year+1900), y=tot_cover, color=color))+
#                 geom_line()+
#                 geom_point()+
#                 facet_grid(site~., scales = "free_y")+
#                 guides(color=FALSE)+
#                 ylab("Mean Percent Cover")+
#                 xlab("Year")+
#                 scale_color_manual(values = brewer.pal(11,"Paired"))
# 
# pgr_plot <- ggplot(data=pgr_data, aes(x=(year+1900), y=pgr, color=color))+
#               geom_line()+
#               geom_point()+
#               facet_grid(site~., scales = "free_y")+
#               guides(color=FALSE)+
#               ylab("Per Capita Growth Rate")+
#               xlab("Year")+
#               scale_color_manual(values = brewer.pal(11,"Paired"))
# full_plot <- grid.arrange(cover_plot, pgr_plot, ncol=2)
```

\pagebreak{}

Figures
-------
```{r concept_fig, echo=FALSE, fig.cap="Conceptual figure outlining the effects of interspecific interactions and environmental stochasticity in large populations where demographic stochasticity is effectively absent (A) and in populations of varying size where demographic stochasticity is present (B).", eval=T}
library(png)
library(grid)
img <- readPNG("./components/synchrony_conceptual_fig.png")
grid.raster(img)
```

```{r read_data, echo=FALSE, eval=T}
output_list <- readRDS("../results/ipm_comp_nocomp_sims.RDS")
mlist <- melt(output_list)
```

```{r figure_1, echo=FALSE, fig.cap="Observed (vertical dashed lines) and IPM simulated (solid density curves) synchrony of species per capita growth rates based on changes in percent cover.", fig.width=6, fig.height=6, fig.width=3, eval=T}
nyrs <- c(max(out_az$stability$num_observations),
          max(out_id$stability$num_observations),
          max(out_ks$stability$num_observations),
          max(out_mt$stability$num_observations),
          max(out_nm$stability$num_observations))

boots <- 100
sites <- sort(table_data$Site)
sites[5] <- "NewMexico"
synch <- matrix(NA, boots, length(sites))

for(do_site in 1:length(sites)){
  full_ipm_outs <- subset(mlist, L2=="ENVINTER")
  site_ipm <- subset(full_ipm_outs, L1==sites[do_site])
  colnames(site_ipm) <- c("year", "species", "cover", "L1", "L2")
  # if(sites[do_site]=="Idaho") site_ipm <- subset(site_ipm, Var2!="ARTR")
  species_list <- unique(site_ipm$species)
  num_spp <- length(species_list)
  for(i in 1:boots){
    begin_year <- sample(x = 1:(max(site_ipm$year)-nyrs[do_site]), 1)
    end_year <- begin_year+nyrs[do_site]
    tmp <- subset(site_ipm, year %in% begin_year:end_year)
    tmp2 <- dcast(tmp, year~species, value.var = "cover")

    # caclulate observed growth rates
    # create lagged data frame to only get observed yearly transitions
    lag_df <- tmp2
    lag_df$lagyear <- lag_df$year+1
    colnames(lag_df)[2:(num_spp+1)] <- paste0(colnames(lag_df)[2:(num_spp+1)],"_t0") 
    
    # merge the lag df with observed
    rm_col <- which(colnames(lag_df)=="year")
    merged_df <- merge(tmp2, lag_df[,-rm_col], by.x = "year", by.y="lagyear")
    transitions <- nrow(merged_df)
    obs_gr <- matrix(nrow=transitions, ncol=num_spp)
    name_ids1 <- which(colnames(merged_df) %in% species_list)
    name_ids2 <- which(colnames(merged_df) %in% paste(species_list, "_t0", sep=""))
    for(ii in 1:transitions){
      obs_gr[ii,] <- as.numeric(log(merged_df[ii,name_ids1]/merged_df[ii,name_ids2]))
    }
    synch[i,do_site] <- as.numeric(community.sync(obs_gr)[1])
  }
}

colnames(synch) <- sites
synch_df <- melt(synch)

obs_pgr_df <- c(as.numeric(out_az$pgr_synchrony[1]),
                as.numeric(out_id$pgr_synchrony[1]),
                as.numeric(out_ks$pgr_synchrony[1]),
                as.numeric(out_mt$pgr_synchrony[1]),
                as.numeric(out_nm$pgr_synchrony[1]))
obs_pgr_df <- data.frame(pgr_synch=obs_pgr_df,
                         Var2=sites)

ggplot()+
  geom_line(data=synch_df, aes(x=value, color=Var2), stat="density", adjust=2)+
  geom_vline(data=obs_pgr_df, aes(xintercept=pgr_synch, color=Var2), linetype=2)+
  facet_wrap("Var2", ncol=1)+
  scale_color_manual(values = c("grey45", "steelblue", "slateblue4", "darkorange", "purple"))+
  guides(color=FALSE)+
  theme_bw()
```

```{r figure_2, echo=FALSE, fig.cap="Results from IPM simulations with difference sources of stochasticity present/absent at each site. DEMO = demographic stochasticity only; ENV = environmental stochasticity only; ENVDEMO = both demograhpic and environmental stochasticity.", fig.width=6, eval=T}
colnames(mlist)[1:3] <- c("year", "species", "cover")
sites <- unique(mlist$L1)
sims <- unique(mlist$L2)
pgr_list <- list()
for(dosite in sites){
  tmp_data <- subset(mlist, L1==dosite)
#   if(dosite=="Idaho"){
#     tmp_data <- subset(tmp_data, species!="ARTR")
#   }
  within_site_list <- list()
  for(dosim in sims){
    tmpsim <- subset(tmp_data, L2==dosim)[c("year", "species", "cover")]
    tmpsynch <- get_ipm_synchrony(tmpsim)
    tmp_pgr_synch <- as.numeric(tmpsynch$pgr_synchrony["obs"])
    within_site_list[[dosim]] <- tmp_pgr_synch
  }
  pgr_list[[dosite]] <- within_site_list
}
pgr_synch <- melt(pgr_list)
expected_synch <- table_data[,c(1,3)]
expected_synch$L2 <- "E(SYNCH)"
colnames(expected_synch) <- c("L1", "value", "L2")
expected_synch <- expected_synch[,c("value", "L2", "L1")]
expected_synch[which(expected_synch[,"L1"]=="New Mexico"),"L1"] <- "NewMexico"

pgr_synch <- rbind(pgr_synch, expected_synch)

# ggplot(pgr_synch, aes(x=L2, y=value, fill=L2))+
#   geom_bar(stat="identity", position=position_dodge(0.9), color="grey")+
#   facet_wrap("L1", scales="free_x")+
#   scale_fill_manual(values = c("grey45", "steelblue", "slateblue4"))+
#   guides(fill=FALSE)+
#   scale_y_continuous(limits=c(0,1))+
#   xlab("Source of stochasticity")+
#   ylab("Species synchrony")

pgrsynch_plot <- ggplot(pgr_synch, aes(x=L2, y=value, color=L1, group=L1))+
  geom_line()+
  geom_point(size=5)+
  scale_color_manual(values = c("grey45", "steelblue", "slateblue4", "darkorange", "purple"),
                     name = "Site")+
  scale_y_continuous(limits=c(0,1))+
  xlab("Simulation")+
  ylab("Species synchrony")+
  theme_bw()

print(pgrsynch_plot)
```

```{r ibm_sims_figure, echo=FALSE, fig.cap="Species synchrony from spatially-explicit IBM simulations with (A,C) and without (B,D) environmental fluctuations and with (A,B) and without (C,D) interspecific interactions. Points represent replicate IBM simulations (out of 20 possible) in which no species went extinct. Lines show linear fits between plot size (proxy for population size) and species synchrony. Demographic stochasticity plays a large role in small populations (small plot sizes) and a smaller role in large populations (large plot sizes).", fig.height=6}
library(png)
library(grid)
img <- readPNG("./components/ibm_sims_fig.png")
grid.raster(img)
```

```{r time_series, eval=FALSE, echo=FALSE, fig.cap="Example time series from the simulations.", eval=F}
ggplot(mlist, aes(x=year, y=(cover*100), color=species))+
  geom_line()+
  facet_grid(L1~L2, scale="free")
```

\pagebreak{}

References
----------