---
layout: 12pt
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{todonotes}

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: true
fontsize: 12pt
geometry: margin=1in

---

Comparing IPM with approximate demographic stochasticity to IBM
===============================================================

Our approach to incorporating demographic stochasticity in integral projection models (IPMs) is new, and thus requires testing.
Individually-based models (IBMs) inherently include demographic stochasticity (e.g., "coin flips" for survival of a genet from a Bernouli trial).
IBMs, then, provide the baseline against which to compare an IPM with our approximation to demogrpahic stochasticity.
If the two models produce similar equilibrium cover and species synchrony, then we can conclude our approximation is valid.
Here we use the Idaho dataset as a test case, and simulate communities from the IPM with demographic stochastisticy and the IBM.
We ignore temporal variation due to random year effects to isolate variation from demographic stochasticity alone. 

```{r figs, echo=FALSE, message=FALSE, warning=FALSE, fig.height=2.5, fig.cap="Density estimates of equilibrium cover from 2,000 iterations from each model."}
library(ggplot2)
library(plyr)
library(reshape2)
ipm_outs <- readRDS("../../results/idaho_ipm_demogstoch_only.RDS")
ibm_outs <- readRDS("../../results/idaho_ibm_demogstoch_only.RDS")
ipm_outs <- as.data.frame(ipm_outs[501:2500,2:4])
ibm_outs <- as.data.frame(ibm_outs[501:2500,5:7])
ipm_outs$model <- "IPM"
ibm_outs$model <- "IBM"
ipm_outs$timestep <- c(1:2000)
ibm_outs$timestep <- c(1:2000)
colnames(ipm_outs) <- c("HECO", "POSE", "PSSP", "model", "timestep")
colnames(ibm_outs) <- c("HECO", "POSE", "PSSP", "model", "timestep")
outs <- rbind(ipm_outs, ibm_outs)

outd <- melt(outs, id.vars = c("model", "timestep"))

ggplot(outd)+
  geom_line(stat="density", aes(x=value*100, color=model))+
  facet_wrap("variable", scales="free")+
  scale_color_manual(values=c("black", "purple"))+
  xlab("equilibrium cover (%)")+
  theme_bw()
```

```{r synch_calcs, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
library(synchrony)
library(xtable)
ipm_outs <- readRDS("../../results/idaho_ipm_demogstoch_only.RDS")
ibm_outs <- readRDS("../../results/idaho_ibm_demogstoch_only.RDS")
ipm_mat <- ipm_outs[501:2500, 2:4]
ibm_mat <- ibm_outs[501:2500, 5:7]

####
####  Synchrony of population size (cover)
####
ipm_synch <- as.numeric(unlist(community.sync(ipm_mat)[1]))
ibm_synch <- as.numeric(unlist(community.sync(ibm_mat)[1]))

####
####  Synchrony of population growth rates
####
sppList <- c("HECO", "POSE", "PSSP")
cov_d <- as.data.frame(ipm_mat)
colnames(cov_d) <- sppList
cov_d$year <- c(1:nrow(cov_d))
lag_d <- cov_d
lag_d$lagYear <- lag_d$year+1
colnames(lag_d)[1:3] <- paste(sppList,".t0", sep="")
lag_d <- lag_d[,-4]
all_d <- merge(cov_d, lag_d, by.x = "year", by.y="lagYear")
transitions <- nrow(all_d)
obs_gr <- matrix(nrow=transitions, ncol=length(sppList))
for(i in 1:transitions){
  obs_gr[i,] <- as.numeric(log(all_d[i,2:4]/all_d[i,5:7]))
}
ipm_gr_synch <- as.numeric(unlist(community.sync(obs_gr[,1:3])[1]))

sppList <- c("HECO", "POSE", "PSSP")
cov_d <- as.data.frame(ibm_mat)
colnames(cov_d) <- sppList
cov_d$year <- c(1:nrow(cov_d))
lag_d <- cov_d
lag_d$lagYear <- lag_d$year+1
colnames(lag_d)[1:3] <- paste(sppList,".t0", sep="")
lag_d <- lag_d[,-4]
all_d <- merge(cov_d, lag_d, by.x = "year", by.y="lagYear")
transitions <- nrow(all_d)
obs_gr <- matrix(nrow=transitions, ncol=length(sppList))
for(i in 1:transitions){
  obs_gr[i,] <- as.numeric(log(all_d[i,2:4]/all_d[i,5:7]))
}
ibm_gr_synch <- as.numeric(unlist(community.sync(obs_gr[,1:3])[1]))


####
####  Make table
####
table_data <- data.frame(Model = c("IPM", "IBM"),
                         Cover_Synch = c(round(ipm_synch,2), round(ibm_synch,2)),
                         PGR_Synch = c(round(ipm_gr_synch,2), round(ibm_gr_synch,2)))
colnames(table_data) <- c("Model", "Cover Sychrony", "Growth Rate Synchrony")
print(xtable(table_data, caption = "Species synchrony of percent cover and per capita growth rates."), type="latex", comment=FALSE, include.rownames=FALSE, caption.placement="top")
```
