---
output: html_document
---
# Checking IPM simulation output
```{r read_data}
library(plyr)
library(reshape2)
library(ggplot2)
library(synchrony)
output_list <- readRDS("../../results/ipm_simulation_lists.RDS")
mlist <- melt(output_list)
```

## Look at simulated time series
```{r time_series}
ggplot(mlist, aes(x=Var1, y=(value*100), color=Var2))+
  geom_line()+
  facet_grid(L1~L2, scale="free")
```

## Run through synchrony library
```{r get_synchs}
library(communitySynchrony)
colnames(mlist)[1:3] <- c("year", "species", "cover")
ts_data <- subset(mlist, L2=="ENVDEMO" & L1=="Arizona")[1:3]
test1 <- get_ipm_synchrony(ts_data = ts_data)
str(test1)
```

## Plot results of simulation scenarios
```{r results_plot}
colnames(mlist)[1:3] <- c("year", "species", "cover")
mlist <- subset(mlist, year>500)
sites <- unique(mlist$L1)
sims <- unique(mlist$L2)
pgr_list <- list()
for(dosite in sites){
  tmp_data <- subset(mlist, L1==dosite)
  if(dosite=="Idaho"){
    tmp_data <- subset(tmp_data, species!="ARTR")
  }
  within_site_list <- list()
  for(dosim in sims){
    tmpsim <- subset(tmp_data, L2==dosim)[c("year", "species", "cover")]
    tmpsynch <- get_ipm_synchrony(tmpsim)
    tmp_pgr_synch <- as.numeric(tmpsynch$pgr_synchrony["obs"])
    within_site_list[[dosim]] <- tmp_pgr_synch
  }
  pgr_list[[dosite]] <- within_site_list
}
pgr_synch <- melt(pgr_list) 

ggplot(pgr_synch, aes(x=L2, y=value, fill=L2))+
  geom_bar(stat="identity", position=position_dodge(0.9), color="grey")+
  facet_wrap("L1")+
  scale_fill_manual(values = c("grey45", "steelblue", "slateblue4"))+
  guides(fill=FALSE)+
  scale_y_continuous(limits=c(0,1))+
  xlab("Source of stochasticity")+
  ylab("Species synchrony")

```

So all sites except Montana show an increase in species synchrony when environmental variation is included in the model. This is probably because they are all perennial grass species in semi-arid grasslands that respond similarly to environmental conditions.


## Comparison with niche differecnes
```{r niches}
niche_diff <- data.frame(site=sites,
                         ND = c(0.58, 0.59, 0.66, 0.69, 0.68))
pgr_subs <- subset(pgr_synch, L2!="ENVDEMO")
pgr_cast <- dcast(pgr_subs, L1~L2, value.var = "value")
synch_diff <- ddply(pgr_cast, .(L1), summarise,
                    value = ENV-DEMO)
niche_synch <- merge(niche_diff, synch_diff, by.x="site", by.y="L1")
ggplot(niche_synch, aes(x=ND, y=value))+
  geom_point(size=5)
```